Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
finished review of Step I

When training is completed, 
we can start separating samples.
To do so,
normality scores $\mathcal{N}(\cdot)$ are used,
defined as the maximum prediction of the rotation classifier:
$\mathcal{N}({\bf\tilde{x}}_i) = \max({\bf\tilde{z}}_i)$.
To predict wheter a sample belongs to the known samples of the target domain $\mathcal{D}_t^{knw}$ or the unknown ones $\mathcal{D}_t^{unk}$ requires picking a threshold $\tilde{\mathcal{N}}$.
The separation is then done as:

@@

When using a multi-head rotation classifier, 
it is required to choose among the $|\mathcal{C}_s|$ possible heads to make the prediction.
Head $R_{1,j}$ is used by choosing $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.

>>>>

When training is completed, 
we can start separating the target samples into known and unknown.
To do so,
{\it normality scores} $\mathcal{N}(\cdot)$ are used,
defined as the maximum prediction of the rotation classifier:
$\mathcal{N}({\bf\tilde{x}}_i) = \max({\bf\hat{z}}_i)$.
Notice that, for each target sample, all the four rotations are applied and the resulting normality score for the sample
is computed as the mean of the four normality scores.
To decide if a target sample belongs to a known semantic class or not, we compare the normality score with a threshold $\tilde{\mathcal{N}}$.

@@

When using a multi-head rotation classifier, 
it is required to choose among the $|\mathcal{C}_s|$ possible heads to make the prediction.
Head $R_{1,j}$ is used where $\displaystyle j = \arg\max_j \{{\bf\hat{y}}_{i, [j]}^t\}_{j=0}^{|\mathcal{C}_s|-1}$
($j$ is the component $j$ of the vector).
